Commutative Character Sheaves

### 2015-09-28 followup.tex
More surgery. Removed intermediate use of CS(G).

\section{Main Definition and Result}

@@

\subsection{Commutative group schemes}

\begin{lemma}\label{lem:commutative}
If $G$ is commutative then the categories $\CCS(G)$ and $\CS(G)$ are equivalent.
\todo{I'm confused. There are extra isomorphisms in the former category, but I think they're equivalent for indirect reasons.}
\end{lemma}

Theorem~\ref{thm:Gab} will be proved by factoring $\CCS(G\ab) \to \CCS(G\ab)$ according to the following diagram, which will be explained below, 
and by showing that each functor is an equivalence.
\[
\begin{tikzcd}
 \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Equivariance}} \\
\CS_G(G)  \arrow{u}{\text{Equivariance}} &&& \CS_{G\ab}(G\ab) \arrow{d}{\text{Commutative group}}  \\
\CS_{G\der}(G) \arrow{u}{\text{Change of Action}} &&& \arrow{lll}{\text{Descent along torsor}}  \CS(G\ab)  \\
\end{tikzcd}
\]

We wish to consider the category $\CS_G(G)$ of $G$-equivariant linear character sheaves on $G$. To that end, in this section we introduce that notion in its general context.

\begin{lemma}\label{lem:equivariant}
$\CCS(G)$ and $\CS_G(G)$ are equivalent.
\end{lemma}
%\begin{proposition}
%Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$. Conversely, if a rank-$1$ character sheaf on $G$ is equivariant for conjugation, then it is commutative. 
%\end{proposition}

\subsection{Descent}

\begin{proof}[Proof of Theorem~\ref{thm:Gab}]
First we must see that $q^*$ factors according to . . . 
\[
\begin{tikzcd}
 \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Lem~\ref{lem:equivariant}}} \\
\CS_G(G)  \arrow{u}{\text{Lem~\ref{lem:equivariant}}} &&& \CS_{G\ab}(G\ab) \arrow{d}{\text{Lem~\ref{lem:commutative}}}  \\
\CS_{G\der}(G) \arrow{u}{\text{Lem~\ref{lem:action}}} &&& \arrow{lll}{\text{Lem~\ref{lem:descent}}}  \CS(G\ab)  \\
\end{tikzcd}
\]
\end{proof}

@@

>>>>

\section{Recollections and definitions}

@@

@@

\section{Descent to the Abelianization}

\subsection{Derived subgroup}

Theorem~\ref{thm:Gab} will be proved by factoring $\CCS(G\ab) \to \CCS(G\ab)$ according to the following diagram, which will be explained below, 
and by showing that each functor is an equivalence.
\[
\begin{tikzcd}
 \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Descent along torsor}} \\
\CCS_G(G)  \arrow{u}{\text{Equivariance}} &&& \arrow{lll}{\text{Change of Action}} \CCS_{G\der}(G) 
\end{tikzcd}
\]

We wish to consider the categories $\CCS_G(G)$ (resp $\CS_G(G)$) of $G$-equivariant commutative character sheaves (linear character sheaves) on $G$. To that end, in this section we introduce that notion in its general context.

\begin{lemma}\label{lem:equivariant}
$\CCS(G)$ and $\CCS_G(G)$ are equivalent.
\end{lemma}
%\begin{proposition}
%Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$. Conversely, if a rank-$1$ character sheaf on $G$ is equivariant for conjugation, then it is commutative. 
%\end{proposition}

\subsection{Descent along torsors}

\begin{proof}[Proof of Theorem~\ref{thm:Gab}]
First we must see that $q^*$ factors according to . . . 
\[
\begin{tikzcd}
 \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Lem~\ref{lem:descent}}} \\
\CCS_G(G)  \arrow{u}{\text{Lem~\ref{lem:equivariant}}} &&& \arrow{lll}{\text{Lem~\ref{lem:action}}} \CCS_{G\der}(G) 
\end{tikzcd}
\]
\end{proof}
